---
title: "Geocoding usage example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Geocoding usage example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Two convenience functions are provided that allows address information to be used as basis for a geocoding lookup that can return coordinates. Let's say address information is provided for an institution or institute that is not present in the GRID database. The following example shows how these geocoding functions can be used to look up geocoding information:

```{r setup}
library(institutions)
library(dplyr)

institutions_download()

# using Nominatim API (Open Street Map)
osm <- 
  geocode_nominatim("Kungliga Tekniska Högskolan") 

# coordinates etc
osm %>% glimpse()
osm %>% select(lat, lon)

# using MapQuest API

mq <- 
  geocode_mapquest(
    street = "Kungliga Tekniska Hogskolan",
    zip = "100 44",
    city = "Stockholm") 

# coordinates etc
mq %>%
  mutate_at(vars(starts_with("admin")), function(x) iconv(x, to = "iso-8859-1")) %>%
  slice(2) %>%  # use only the second result
  glimpse()

#browseURL(mq$)

```
